---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# OneTwoSamples

<https://doi.org/10.32614/CRAN.package.OneTwoSamples>

<!-- badges: start -->
[![DOI](https://img.shields.io/badge/doi-10.32614/CRAN.package.OneTwoSamples-blue.svg)](https://doi.org/10.32614/CRAN.package.OneTwoSamples)
[![CRAN status](https://www.r-pkg.org/badges/version/OneTwoSamples)](https://CRAN.R-project.org/package=OneTwoSamples)
<!-- badges: end -->

The goal of OneTwoSamples is to introduce an R function one_two_sample() which can deal with one and two (normal) samples, Ying-Ying Zhang, Yi Wei (2012) <doi:10.2991/asshm-13.2013.29>. 
For one normal sample x, the function reports descriptive statistics, plot, interval estimation and test of hypothesis of x. For two normal samples x and y, the function reports descriptive statistics, plot, interval estimation and test of hypothesis of x and y, respectively. It also reports interval estimation and test of hypothesis of mu1-mu2 (the difference of the means of x and y) and sigma1^2 / sigma2^2 (the ratio of the variances of x and y), tests whether x and y are from the same population, finds the correlation coefficient of x and y if x and y have the same length.

## Installation

You can install the released version of OneTwoSamples from [CRAN](https://CRAN.R-project.org) with:

```{r, eval = FALSE}
install.packages("OneTwoSamples")
```

You can install the development version of OneTwoSamples from [github](https://github.com) with:

```{r, eval = FALSE}
devtools::install_github("fbertran/OneTwoSamples")
```

## Examples

This is a basic example which shows you how to solve a common problem:

```{r example}
library(OneTwoSamples)
```

## One sample
```{r}
x=rnorm(10, mean = 1, sd = 0.2); x
```

## one_sample(x, ...) == one_two_sample(x, ...)
```{r}
one_sample(x, mu = 1, sigma = 0.2, side = 1)
one_two_sample(x, mu = 1, sigma = 0.2, side = 1)
```

```{r}
one_sample(x, sigma = 0.2, side = 1)
one_two_sample(x, sigma = 0.2, side = 1)
```

```{r}
one_sample(x, mu = 1, side = 1)
one_two_sample(x, mu = 1, side = 1)
```

```{r}
one_sample(x)
one_two_sample(x)
```

## Two samples
```{r}
set.seed(1)
x=rnorm(10, mean = 1, sd = 0.2); x
y=rnorm(20, mean = 2, sd = 0.3); y
y2=rnorm(20, mean = 2, sd = 0.2); y2
```

## sigma1, sigma2 known; mu1, mu2 known
```{r}
one_two_sample(x, y, sigma = c(0.2, 0.3), mu = c(1, 2))
```

## sigma1 = sigma2 unknown; mu1, mu2 known
```{r}
one_two_sample(x, y2, var.equal = TRUE, mu = c(1, 2))
```

## sigma1 != sigma2 unknown; mu1, mu2 known
```{r}
one_two_sample(x, y, mu = c(1, 2))
```

## sigma1, sigma2 known; mu1, mu2 unknown
```{r}
one_two_sample(x, y, sigma = c(0.2, 0.3))
```

## sigma1 = sigma2 unknown; mu1, mu2 unknown
```{r}
one_two_sample(x, y2, var.equal = TRUE)
```

## sigma1 != sigma2 unknown; mu1, mu2 unknown
```{r}
one_two_sample(x, y)
```

